PLUNGER: Reproducing FLUSH+RELOAD: A High-Resolution, Low-Latency Side Channel Attack On GnuPG

### 2014-12-17 paper/paper.tex
Adjust the size of the trailing lobster
And reword the footnote a bit.

Windows, Linux, and possibly OS X\footnote{It is unclear whether or not OS X
implements page deduplication, but as far as we can tell it does} also perform a
more aggressive form of page sharing known as \textit{page deduplication}. With
this scheme, the operating system scans memory pages during idle CPU cycles, and
looks for pages that are identical in content. It collapses those pages into a
single page that is then shared by all processes that were accessing those
identical pages. As a result of this page deduplication scheme, processes may be
unknowingly or unintentionally sharing memory with one another. However, to
prevent malicious access to the shared pages, the operating system maps shared
pages as copy-on-write; that is, when a process wishes to write to a page, it
must first make a local copy for itself that it can safely modify. When a write
is requested, the CPU traps to the kernel, which then remaps a copy of the
desired page for the process requesting the write, and then returns control to
the calling process. Read operations in this scheme do not require such a trap
as they do not modify the targeted page and are therefore ``safe''.

@@

\hspace*{7cm} 
\lob[lobblue, scale=1.5]{83} \hfill

>>>>

Windows, Linux, and possibly OS X\footnote{It is unclear if OS X
implements page deduplication, but there are indications that it does.} also perform a
more aggressive form of page sharing known as \textit{page deduplication}. With
this scheme, the operating system scans memory pages during idle CPU cycles, and
looks for pages that are identical in content. It collapses those pages into a
single page that is then shared by all processes that were accessing those
identical pages. As a result of this page deduplication scheme, processes may be
unknowingly or unintentionally sharing memory with one another. However, to
prevent malicious access to the shared pages, the operating system maps shared
pages as copy-on-write; that is, when a process wishes to write to a page, it
must first make a local copy for itself that it can safely modify. When a write
is requested, the CPU traps to the kernel, which then remaps a copy of the
desired page for the process requesting the write, and then returns control to
the calling process. Read operations in this scheme do not require such a trap
as they do not modify the targeted page and are therefore ``safe''.

@@

\hspace*{7cm}
\lob[lobblue, scale=1.3]{83} \hfill
